---
title: "r_tutorial2"
author: "Francisco A. Castro Rivera"
date: "`r format(Sys.time(), '%Y-%b-%d. %I:%M %p')`"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      results = "markup")

```

## R Tutorial #2

install.packages("gapminder")
install.packages("dplyr")
library(gapminder)
library(dplyr)


data(gapminder)
head(gapminder)


data(gapminder)
gapminder
View(gapminder)

### Q1. What class is the gapminder dataset? 


```{r}
library(gapminder)
class(gapminder)
```

### Q2. Filter a section of gapminder with a life expectancy smaller than 29

```{r, message= FALSE}
library(gapminder)
library(dplyr)
gapminder |> 
  filter(lifeExp < 29)
```

### Q3. Filter the dataset for the country Rwanda and for years greater than 1979.

```{r}
library(gapminder)
library(dplyr)
gapminder |> 
 filter(country == "Rwanda") |> 
 filter(year > "1979")
```

### Q4. Create a new dataset from gapminder excluding the column gdpPercap.

```{r}
library(gapminder, dplyr)
gapminder |> 
  select(!(gdpPercap))
```

### Q5 Arrange the dataset in ascending order of lifeExp.

```{r}
library(gapminder, dplyr)
gapminder |> 
  arrange(lifeExp)
```
### Q6 Arrange the dataset in descending order of lifeExp.

```{r}
library(gapminder, dplyr)
gapminder |> 
  arrange(desc(lifeExp))
```

### Q7 Create a new dataset with only the columns year and lifeExp.

```{r}
library(gapminder, dplyr)
subset1 <- 
  gapminder |> 
  select(year, lifeExp)

subset1

```

### Q8 Filter the dataset for the country Cambodia and show only the columns year and lifeExp.

```{r}
library(gapminder, dplyr)
gapminder |> 
  filter(country == "Cambodia") |> 
  select(year, lifeExp)

```

### Q9 Select only the countries in Africa.

```{r}
library(gapminder, dplyr)
gapminder |> 
  filter(continent == "Africa")
```

### Q10 Create a new column called lifeExp_months that shows life expectancy in months. 
```{r}
library(gapminder, dplyr)
gapminder |> 
  select(-pop , -year) |> 
  mutate(lifeExp_months = lifeExp * 12.00)

#Not super sure about this one...
#I'll have to delete some columns so that the table fits the screen...
```



